### 2021-04-06 assertions/doc/thesis-bernhardt/chapters/1-introduction.tex
Extension of Michelson/Introduction chapter 4
Modular approach

\section{A distributed approach for assertion checking}
A more efficient way to solve the issue at hand could be to engage the validators of the blockchain into a distributed effort to find a counterexample. If no counterexample could be found by any validator, the assumption is considered to be valid and the execution of the contract may resume. On the other hand, an identified counterexample is made public on the peer-to-peer network and thus cancels the contract execution (i.e., the transaction fails). \\
In order to find a counterexample to the assertion, the formula in \eqref{eq:prime} has to be transformed to its negation:
\begin{equation}\label{eq:prime_neg}
	(\exists n) (2 \le n \le \sqrt{p}) \wedge (p \% n) = 0
\end{equation}

Each validator then checks the inverse property $(p \% n) = 0$ point-wise for some random $n$ within the given boundaries $2 \le n \le \sqrt{p}$. If a validator finds a counterexample, i.e., a value for $n$ where the reminder is $0$, it posts an objection to the network. For each involved validator, the constant cost of generating one random number and calculating one division have to be paid, which is independent from $p$. \todo{Change if not true} \\
However, distributed assertion checking is not only applicable for parameters or properties of dynamic size. Another example given in \cite{thiemann_2020} shows a contract that expects an array of integers sorted in ascending order:

@@

Since the validators sample the domain randomly, the absence of a counterexample doesn't prove that the assumption is correct; the validation is only probabilistic and the reliability depends on the number of validators in the network. This corresponds to the principle of Bloom filters, where a queried element is either ``certainly not'' or ``possibly'' a member of a defined set \cite{blustein_bloom_2002}. In the case of assertion checking, we consider the assumption to be either definitely not or possibly valid. The probability of false positives in Bloom filters is an approximate function of the filter size and the number of inserted elements, supposing an optimal number of hash functions have been implemented. Tuning these parameters is a trade-off between making the filter more reliable, i.e., lowering its error rate, and space efficiency \cite{blustein_bloom_2002}. The same applies, with some reservations, to distributed assertion checking: less samples keep the gas consumption to a minimum, whereas more samples increase the probability that an existing counterexample is found. Refering to the example of sorted lists,  the probability of false positives depends on the size of the list $a$ and the number of validators $m$.\\
The importance of the former parameter becomes obvious when looking at the worst case scenario of the same example. Assume the array is unsorted at exactly one position - the probability that the each of the $m$ validators independently check this position is $\frac{1}{|a|}$, while all of them checking any other position $\frac{|a|-1}{|a|}$. If the random generator chooses each value for $n$ independently from a uniform distribution, the probability that the counterexample is not detected by any validator converges to 0 if the number of validators approaches infinity \cite{thiemann_2020}:
\begin{equation}\label{eq:limes_validators}
	\lim_{m\to\infty} \left(\frac{|a|-1}{|a|}\right)^m = 0
\end{equation}

>>>>

\section{A distributed approach for assertion checking}
A more efficient way to solve the issue at hand could be to engage the validators of the blockchain into a distributed effort to find a counterexample. If no counterexample could be found by any validator, the assumption is considered to be valid and the execution of the contract may resume. On the other hand, an identified counterexample is made public on the peer-to-peer network and thus cancels the contract execution (i.e., the transaction fails). \\
In order to find a counterexample, the formula in \eqref{eq:prime} has to be transformed to its negation:
\begin{equation}\label{eq:prime_neg}
	(\exists n) (2 \le n \le \sqrt{p}) \wedge (p \% n) = 0
\end{equation}

Each validator then checks the inverse property $(p \% n) = 0$ point-wise for some random $n$ within the given boundaries $2 \le n \le \sqrt{p}$. If a validator finds a counterexample, i.e., a value for $n$ where the reminder is $0$, it posts an objection to the network. For each involved validator, the constant cost of generating one random number and calculating one division have to be paid, which is independent from $p$. \\
However, distributed assertion checking is not only applicable for parameters or properties of dynamic size. Another example given in \cite{thiemann_2020} shows a contract that expects an array of integers sorted in ascending order:

@@

Since the validators sample the domain randomly, the absence of a counterexample doesn't prove that the assumption is correct; the validation is only probabilistic and the reliability depends on the number of validators in the network. This corresponds to the principle of Bloom filters, where a queried element is either ``certainly not'' or ``possibly'' a member of a defined set \cite{blustein_bloom_2002}. In the case of assertion checking, we consider the assumption to be either definitely not or possibly valid. The probability of false positives in Bloom filters is an approximate function of the filter size and the number of inserted elements, supposing an optimal number of hash functions have been implemented. Tuning these parameters is a trade-off between making the filter more reliable, i.e., lowering its error rate, and space efficiency \cite{blustein_bloom_2002}. The same applies, with some reservations, to distributed assertion checking: less samples keep the gas consumption to a minimum, whereas more samples increase the probability that an existing counterexample is found. Referring to the example of sorted lists,  the probability of false positives depends on the size of the list $a$ and the number of validators $m$.\\
The importance of the former parameter becomes obvious when looking at the worst case scenario of the same example. Assume the array is unsorted at exactly one position - the probability that the each of the $m$ validators independently check this position is $\frac{1}{|a|}$, while all of them checking any other position $\frac{|a|-1}{|a|}$. If the random generator chooses each value for $n$ independently from a uniform distribution, the probability that the counterexample is not detected by any validator converges to 0 if the number of validators approaches infinity \cite{thiemann_2020}:
\begin{equation}\label{eq:limes_validators}
	\lim_{m\to\infty} \left(\frac{|a|-1}{|a|}\right)^m = 0
\end{equation}

### 2021-04-06 assertions/doc/thesis-bernhardt/chapters/3-offline_design.tex
Modular approach

\subsubsection{Building smart random generators}
In order to assign each explicit bound to its appropriate quantifier, the formula has be skimmed for atomic constraints that contain predicate (bound) variables. They're then moved and assigned to the quantifier that bounds the variable. If the constraint contains more than one bound variable, it is assigned to the quantifier with the highest depth in the order of quantifiers, as they depend on the generated value(s) of the other variable(s). \\
Revisiting the formula from \eqref{eq:sorted_v2}, its premise can be considered as a conjunction of the four constraints
\begin{itemize}
\itemsep-1em
\item $0 \leq n$
\item $n < |a| $
\item $n \le m$ and
\item $m < |a|$.
\end{itemize}
Applying the rules given above after negating the formula, the constraints are assigned to the quantifiers as follows:
\begin{equation}\label{eq:sorted_v2_bounds}
	(\exists n : int, 0 \leq n \wedge n < |a|])(\exists m : int, m > n \wedge m < |a|) \text{ } a[n] > a[m]
\end{equation}
Ultimately, the quantifiers are then translated to the corresponding random generators as indicated in \lstref{lst:rand}.
\begin{lstlisting}[label=lst:rand]
n = random(0, size(list))
m = random(n, size(list))
\end{lstlisting}
While conjunctions can be handled easily, other operators make it more difficult to derive efficient random generators. Consider the following constraints:
\begin{itemize}
\itemsep-0.7em
\item[1)] $(\forall n : int) (n < 10 \lor n > 20) ...$
\item[2)] $(\forall n : int) (n \ne 10) ...$
\item[3)] $(\forall n : int) (n = 10) ...$
\end{itemize}
Constraint 1) complicates restricting the random generator in several ways. Firstly, it separates the domain into two disjoint sub-domains, which requires defining a random generator for each range and another one to decide which one is called. Secondly, the operands of a disjunction cannot be considered separately when more than one bound variable is involved. For the predicate variable whose random generator is executed first, the domain restriction is optional, while the generation of the following random values depend on the previous result. Similarly to 1), constraint 2) splits the domain into sub-domains. To keep it simple for the time being, restrictions formulated with these operators are kept as part of the assertion code rather than used as constraints for the generators. Consequently, some validators may generate irrelevant values when checking the assertion and, depending on the size of the gap between the sub-domains, this can significantly decrease the reliability of this kind of assertion checking. Thus, further developed iterations should handle and translate them accordingly.\\
Constraint 3) effectively makes the quantifier, which binds $n$, obsolete. Adding this constraint to the respective generator will at least not affect the reliability, but a future improvement could be to optimize the assertion by replacing all occurrences of the bound variable with the assigned value and removing the quantification.

@@

\subsubsection{Central instance assigning values}
For this approach, the tool-chain would need to generate a separate contract that is called by the miners and validators as a proxy. This contract would then, for instance, generate a number using a modulo-n counter and pass this number as an additional parameter to the assertion code. The random generators would be omitted accordingly. However, this works only as expected if there are no simultaneous transactions calling the contract, otherwise it cannot be guaranteed that all elements have been checked for each of the transactions. If and how this issue can be solved will not be discussed further in this thesis.

>>>>

\subsubsection{Building smart random generators}
In order to assign each explicit bound to its appropriate quantifier, the formula has be skimmed for atomic constraints that contain predicate (bound) variables. They're then moved and assigned to the quantifier that bounds the variable. If the constraint contains more than one bound variable, it is assigned to the quantifier with the highest depth in the order of quantifiers, as they depend on the generated value(s) of the other variable(s). \\
Revisiting the formula from \eqref{eq:sorted_v2}, its premise can be considered as a conjunction of the four constraints
\begin{itemize}
\itemsep-1em
\item $0 \leq n$
\item $n < |a| $
\item $n \le m$ and
\item $m < |a|$.
\end{itemize}
Applying the rules given above after negating the formula, the constraints are assigned to the quantifiers as follows:
\begin{equation}\label{eq:sorted_v2_bounds}
	(\exists n : int, 0 \leq n \wedge n < |a|])(\exists m : int, m > n \wedge m < |a|) \text{ } a[n] > a[m]
\end{equation}
Ultimately, the quantifiers are then translated to the corresponding random generators, drafted in pseudocode:
\begin{lstlisting}[label=lst:rand, numbers=none]
n = random(0, size(list))
m = random(n, size(list))
\end{lstlisting}
While conjunctions can be handled easily, other operators make it more difficult to derive efficient random generators. Consider the following constraints:
\begin{itemize}
\itemsep-0.7em
\item[1)] $(\forall n : int) (n < 10 \lor n > 20) ...$
\item[2)] $(\forall n : int) (n \ne 10) ...$
\item[3)] $(\forall n : int) (n = 10) ...$
\end{itemize}
Constraint 1) complicates restricting the random generator in several ways. Firstly, it separates the domain into two disjoint sub-domains, which requires defining a random generator for each range and another one to decide which one is called. Secondly, the operands of a disjunction cannot be considered separately when more than one bound variable is involved. For the predicate variable whose random generator is executed first, the domain restriction is optional, while the generation of the following random values depend on the previous result. Similarly to 1), constraint 2) splits the domain into sub-domains. To keep it simple for the time being, restrictions formulated with these operators are kept as part of the assertion code rather than used as constraints for the generators. Consequently, some validators may generate irrelevant values when checking the assertion and, depending on the size of the gap between the sub-domains, this can significantly decrease the reliability of this kind of assertion checking. Thus, further developed iterations should handle and translate them accordingly.\\
Constraint 3) effectively makes the quantifier, which binds $n$, obsolete. Adding this constraint to the respective generator will at least not affect the reliability, but a future improvement could be to optimize the assertion by replacing all occurrences of the bound variable with the assigned value and removing the quantification.

@@

\subsubsection{Central instance assigning values}
For this approach, the tool-chain would need to generate a separate contract that is called by the miners and validators as a proxy. This contract would then, for instance, generate a number using a modulo-n counter and pass this number as an additional parameter to the assertion code. The random generators would be omitted accordingly. However, this works only as expected if there are no simultaneous transactions calling the contract, otherwise it cannot be guaranteed that all elements have been checked for each of the transactions. If and how this issue can be solved will not be discussed further in this thesis.
\todo{Serializes tests -> see expose rejected ideas}

### 2021-04-06 assertions/doc/thesis-bernhardt/chapters/4-offline_design_tezos.tex
Modular approach

@@

\subsection{Approach 1: Monolithic contract}
In the monolithic approach, a new contract is built using both the assertion and parent code as input. As is outlined in \figref{fig:monolithic_orchestration_basic}, the assertions can either be appended to the original contract as separate entrypoints or by prepending them to the code of the respective entrypoint. This tightly couples and unites the code in one self-contained unit.
\begin{figure}[!htb]
\subfloat[Appending assertions as separate entrypoints]{\includegraphics[width=0.5\textwidth]{figures/4-offline_tezos/monolithic_ep.jpg}}
\quad
\subfloat[Inserting the assertion code into the original entrypoint]{\includegraphics[width=0.5\textwidth]{figures/4-offline_tezos/monolithic_insert.jpg}}
\caption{Approaches for assembling a monolithic contract}
\label{fig:monolithic_orchestration_basic}
\end{figure}
While the link between assertion and contract code is already given in a), the entrypoint and assertions in b) still need to be coupled, as it is not inherent which entrypoint represents a normal and which the respective assertion. For this reason, assertion entrypoints need to have fixed name pattern, s.t. it is derivable from the original entrypoint. As a proposal, the tag of the assertion is the tag of its parent entrypoint suffixed with a \texttt{\_a}, e.g. \texttt{A\_a} for entrypoint \texttt{A}. The baker can then execute the contract normally by calling the original entrypoint and prompt the validators to execute the assertion separately. \\
Both approaches, however, do not yet provide any means to have validators execute the assertions $n$ times. Since only the contract itself knows how to calculate $n$ (as per the range(s) of the random generator(s)), it cannot be passed to the validators as a parameter to the validation request. Instead, the contract itself needs a test run manager which handles this. A test run manager can either be implemented as another entrypoint, say \texttt{A\_m}, which then calls \texttt{A\_a} (or \texttt{A} in case of a)) $n$ times as an internal transaction. Another possibility is to create a separate manager contract that acts as a proxy, contains the manager code and internally calls the monolithic contract. This solution is a hybrid of the monolithic and modular approach. The section covering the modular approach describes in more detail how it is implemented.\\
It's important to realize that neither baker nor validators can differentiate between entrypoints that have an associated assertion and those that do not. In order to avoid transaction failures caused by calling assertions that do not exist, the compiler has to add dummy managers for empty assertions that call the actual contract code immediately.\\
% Description figures
% -> txa special transaction type
% managers use internal transactions to call contract n times
% depending on protocol, validators use normal tx or another special tx type
% req message needs to contain the derived name of the assertion ep -> derivation needs to be part of the "assertion mode". is this possible?
% veto message: the txa op hash it refers to, an instance of a counterexample (not yet clear how this looks like)

\begin{figure}[h]
\centering
  \includegraphics[width=0.7\textwidth]{figures/4-offline_tezos/interaction_monolithic.jpg}
	\caption{Interaction with a monolithic contract}
	\label{fig:interaction_monolithic}
\end{figure}

@@

\subsubsection{Evaluation}
Generell:
- parent code has to be modified
	+ show code example
	+ decompilation necessary
	+ compilation is more complex
- doesn't work if the parent code is already originated
- inflexible -> tightly coupled code
	+ if the assertion code changes, the whole contract has to be reoriginated

ep assert + ep manager
+ baker can call basic ep; validators call manager
	-> cost efficient; contract is only executed once
- only works with explicit ep -> parameter types!
- complex compilation (1-2 eps per ep more)
- readability

no ep assert + ep manager
- contract code is also executed n times
- only works with explicit ep -> parameter types!
+ bypassing assertion not possible!
+ less eps more readable? (aber nur bisschen)

ep assert + contract manager
+ less complex compilation -> just copy assertion code before the actual code (less entrypoint handling)
+ if manager also has eps A and A\_m, the code and assertions can also be called separately
+ modularity -> readability, a bit more flexibility (if manager code changes)
- \^ even more eps -> 2-3 eps more
- more boilerplate, more origination costs

no ep assert + contract manager
- contract code is also executed n times
+ bypassing assertion not possible!
+ less complex compilation -> just copy assertion code before the actual code (less entrypoint handling)
+ modularity

what happens to calls to default?

\begin{itemize}
\item Assertions are appended to the parent as separate entry points
\item Parent contract has to be modified (parameter type \& addendum)
\item Problems/Drawbacks:
	\begin{itemize}
	\item entrypoint names necessary - otherwise no unambiguous assignment
	\item parameter types of original ep \& assertion ep are different
	\item e.g. \%A and \%A\_a cannot be called with the same parameter (if not called explicitly; ref. \ref{lst:mono_unnamed} line 24, 25.)
	\item Possible solution:
		\begin{itemize}
		\item all eps in the parent and assertion contract need to have a \%name \verb|->| calling both eps explicitly allows using the same parameter (ASAIK) ; ref. \ref{lst:mono} line 24, 25.
		\item Assign dummy names if none are given - effort?
		\item what to do with calls to \%default?
			\begin{itemize}
			\item Baker would need to
			\item 1) look up entrypoints of contract 
			\item 2) check which type matches \& find out the ep name
			\item 3) derive assertion ep name from that
			\end{itemize}
		\item how to assign entry points given without names in .tza to their respective parent eps? \ref{lst:mono_unnamed} line 10, 11.
		\end{itemize}
	\end{itemize}
\item EP names of the assertion code need to have a fixed pattern, s.t. the bakers know how to call them
\item Similarly to strategy 1, there probably needs to be "empty" assertion code for normal eps
\end{itemize}

%\ref{fig:separate_contract_v2}:
%\begin{figure}[h]
%	\centering
%  \includegraphics[width=\textwidth]{assembly_monolith}
%	\caption{Interaction with a monolithic contract}
%	\label{fig:monolithic_contract}
%\end{figure}

%\lstinputlisting[label=lst:mono, caption=Monolithic assembly w/ ep names, numbers=left]{monolithic.tz}
%\lstinputlisting[label=lst:mono_unnamed, caption=Monolithic assembly w/o ep names, numbers=left]{monolithic_unnamed.tz}

\subsection{Approach 2: }

>>>>

\todo{Add mempool? If Blockchain protocol is outlined}

@@

\subsection{Approach 1: Monolithic contract}
In the monolithic approach, a new contract is built using both the assertion and parent code as input. As is outlined in \figref{fig:monolithic_orchestration_basic}, the assertions can either be appended to the original contract as separate entrypoints or by prepending them to the code of the respective entrypoint. This tightly couples and unites the code in one self-contained unit.
\begin{figure}[!htb]
\subfloat[Appending assertions as separate entrypoints]{\includegraphics[width=0.5\textwidth]{figures/4-offline_tezos/pipeline_output_mono_ep_basic.jpg}}
\quad
\subfloat[Inserting the assertion code into the original entrypoint]{\includegraphics[width=0.5\textwidth]{figures/4-offline_tezos/pipeline_output_mono_basic.jpg}}
\caption{Approaches for assembling a monolithic contract}
\label{fig:monolithic_orchestration_basic}
\end{figure}
While the link between assertion and contract code is already given in a), the entrypoint and assertions in b) still need to be coupled, as it is not inherent which entrypoint represents a normal and which the respective assertion. For this reason, assertion entrypoints need to have fixed name pattern, s.t. it is derivable from the original entrypoint. As a proposal, the tag of the assertion is the tag of its parent entrypoint suffixed with a \texttt{\_a}, e.g. \texttt{A\_a} for entrypoint \texttt{A}. The baker can then execute the contract normally by calling the original entrypoint and prompt the validators to execute the assertion separately. \\
Both approaches, however, do not yet provide any means to have validators execute the assertions $n$ times. Since only the contract itself knows how to calculate $n$ (as per the range(s) of the random generator(s)), it cannot be passed to the validators as a parameter to the validation request. Instead, the contract itself needs a test run manager which handles this. A test run manager can either be implemented as another entrypoint, say \texttt{A\_m}, which then calls \texttt{A\_a} (or \texttt{A} in case of a)) $n$ times as an internal operation. When extending the diagram for a) with the manager, the pipeline output thus look as shown in \figref{fig:monolithic_orchestration}. The output for b) is analogue.
\begin{figure}[h]
\centering
  \includegraphics[width=0.5\textwidth]{figures/4-offline_tezos/pipeline_output_mono_ep.jpg}
	\caption{Monolithic assembly with separate entrypoints for manager and assertion}
	\label{fig:monolithic_orchestration}
\end{figure}
Another possibility is to create a separate manager contract that acts as a proxy, contains the manager code and internally calls the monolithic contract. This solution is a hybrid of the monolithic and modular approach. The section covering the modular approach describes in more detail how it is implemented.\\
It's important to realize that neither baker nor validators can differentiate between entrypoints that have an associated assertion and those that do not. In order to avoid transaction failures caused by calling assertions that do not exist, the compiler has to add dummy managers for empty assertions that call the actual contract code immediately. \lstref{lst:manager} drafts the manager code for entrypoints with and without assertions in pseudocode. 
\begin{lstlisting}[label=lst:manager, caption=Implementation of the manager in pseudocode]
%A (i : int) {
	call(parent.A, i)
}

%A_m (i : int) {
	n = compute_n(i)
	Do j = 1 to n:
		call(parent.A_a, i)
}

%B (i : int) {
	call(parent.B, i)
}

%B_m (i : int) {
	call(parent.B, i)
}
\end{lstlisting}

\figref{fig:interaction_monolithic} and \ref{fig:interaction_monolithic_managertz} depict the interaction of the baker and validators with the resulting contracts on the blockchain for a variant using a single monolithic contract versus a hybrid solution. After calling a contract that includes an assertion, the baker has to keep the transaction in its mempool, a buffer where a node keeps prevalidated transactions not yet included in a block \todo{remove explanation if added to Tezos chapter}. Before it can be included, the transaction has to be kept there for a minimum amount of time, s.t. the validators have enough time to validate the assertion \todo{refer to blockchain protocol chapter if there is one}. The bakers therefore need to execute such transactions in a dedicated ``challenge'' mode, which could be signalled by using a special operation type to call such contracts. Operation types in Tezos are, i.a., transactions, originations or endorsements. By adding, for instance, a special transaction type (abbreviated by \texttt{txa} in the interaction diagrams), bakers can differentiate between normal transactions and those with assertions.
\begin{figure}[h]
\centering
  \includegraphics[width=0.7\textwidth]{figures/4-offline_tezos/interaction_monolithic.jpg}
	\caption{Interaction with a monolithic contract}
	\label{fig:interaction_monolithic}
\end{figure}

@@

After prevalidating a transaction in the challenge mode, the baker then sends a request to the network to check the associated assertion. The request contains the address of the monolithic contract or manager, the operation hash (oph) of the prevalidated transaction, the derived entrypoint tag of the assertion and the parameter. The operation hash is used to relate a counterexample to the respective transaction. Upon receiving such a request, the validators call the assertion manager; what type of operation is used for is an open question for the protocol design. For efficiency, at most the test runs detecting a counterexample should be recorded on the blockchain, which would not be the case if validators use standard transactions. What has been left out so far in the offline design is the representation of a counterexample. \secref{} briefly discusses this as an open question and follow-up of this thesis \todo{secref}.

\subsubsection{Evaluation of the monolithic approach}
The presented implementations of the monolithic approach each have strengths and weaknesses. Generally, they all share a pivotal disadvantage - they require a modification of the parent contract. This not only complicates the compilation process by requiring a decompilation of the parent code and an interweaving of the assertion code, but it also restricts the integration of assertions to contracts that have not yet been originated on the blockchain. \lstref{lst:mono} shows the skeleton of a monolithic contract that results from the given parent and assertion contract; both the parameter type and the branching of the code body have to be adapted. Another problem are contract invocations using the default entrypoint: firstly, the derivation of the entrypoint for the assertion becomes considerably more complex, as no explicit tag is given. Secondly, the parameter cannot be passed unmodified to the assertion, because the parameter types in respect to the default entry point do not match. For instance, invoking the default entrypoint of \texttt{example\_monolithic.tz} (\lstref{lst:mono}) with parameter \texttt{Left 4} calls \texttt{A}, but the respective assertion \texttt{A\_a} expects the value as \texttt{Left (Left 4)}. \\
Due to the tight coupling of parent and assertion code, this approach is also inflexible, since adaptions to either part require a recompilation and new origination of the whole code.
\lstinputlisting[label=lst:mono, caption=Skeleton of a monolithic contract in Michelson, numbers=left]{listings/monolithic.tz}

The distinct advantages and disadvantages of each combination of given implementation approaches are described briefly in the following matrix in \tabref{tab:mono_eval}.
\begin{table}[h]
	\centering
	\newcommand{\tabitem}{~~\llap{\textbullet}~~}
	\caption{Advantages and disadvantages of monolithic implementations}
	\label{tab:mono_eval}
	\subfloat[Monolithic w/ manager and assertion entrypoints] {
		\centering
		\begin{tabular}{ | p{0.5\linewidth} | p{0.5\linewidth} |}
		\hline
		\thead{Advantages} & \thead{Disadvantages} \\ \hline
		\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
		\item Contract and assertion can be called separately $\rightarrow$ parent code is only executed once
		\end{itemize} &
		\begin{itemize}[leftmargin=*, noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
		\item More complex compilation; adds 1-2 entrypoints per native entrypoint
		\item Less readability
		\end{itemize} \\ \hline
		\end{tabular}
	}

	\subfloat[Monolithic w/ manager entrypoints and prepended assertion] {
		\centering
		\begin{tabular}{ | p{0.5\linewidth} | p{0.5\linewidth} |}
		\hline
		\thead{Advantages} & \thead{Disadvantages} \\ \hline
		\begin{itemize}[leftmargin=*, noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
		\item Bypassing the assertion is not possible
		\end{itemize} &
		\begin{itemize}[leftmargin=*, noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
		\item Cost inefficient - validators execute the assertion + code $n$ times
		\item Also only works with explicit entrypoint tags
		\end{itemize} \\ \hline
		\end{tabular}
	}

	\subfloat[Hybrid w/ manager and assertion entrypoints] {
		\centering
		\begin{tabular}{ | p{0.5\linewidth} | p{0.5\linewidth} |}
		\hline
		\thead{Advantages} & \thead{Disadvantages} \\ \hline
		\begin{itemize}[leftmargin=*, noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
		\item Contract and assertion can be called separately
		\item Modularity $\rightarrow$ manager contract can be adapted independently
		\item Readability
		\end{itemize} &
		\begin{itemize}[leftmargin=*, noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
		\item Higher initial origination costs due to more boilerplate code
		\end{itemize} \\ \hline
		\end{tabular}
	}

	\subfloat[Hybrid w/ manager entrypoints and prepended assertion] {
		\centering
		\begin{tabular}{ | p{0.5\linewidth} | p{0.5\linewidth} |}
		\hline
		\thead{Advantages} & \thead{Disadvantages} \\ \hline
		\begin{itemize}[leftmargin=*, noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
		\item Bypassing the assertion is not possible
		\item Modularity
		\item Readability
		\end{itemize} &
		\begin{itemize}[leftmargin=*, noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
		\item Cost inefficient - validators execute the assertion + code $n$ times
		\item Higher initial origination costs due to more boilerplate code
		\end{itemize} \\ \hline
		\end{tabular}
	}
\end{table}

\subsection{Approach 2: Modular contracts}
With the modular approach, the assertion manager and each of the assertions are originated as separate contracts on the blockchain. The manager mirrors the interface of the parent contract, while each assertion each only has a single entrypoint which expects the raw parameter type. Due to the ``outsourcing'' of the assertion code, the parent contract remains pure and does not have to be modified. Similar to the hybrid solution from the last section, the manager calls the respective assertion contract $n$ times as an internal operation before calling the actual contract. In the case of empty assertions, it calls the parent contract immediately. Correspondingly, the pipeline outputs 1-$m$ contracts, where $m$ is the amount of entrypoints with an associated assertion, as depicted in \figref{fig:modular_assembly}.
\begin{figure}[h]
\centering
  \includegraphics[width=0.9\textwidth]{figures/4-offline_tezos/pipeline_output_modular.jpg}
	\caption{Modular assembly of assertion and manager code}
	\label{fig:modular_assembly}
\end{figure}

In order to link the separate contracts to each other, the manager needs to know the addresses of the other contracts, which ultimately entails a fixed origination order. The independent assertion and parent contract(s) have been originated first, so that their addresses can be passed to the manager as initial storage values. If the storage is structured as a map from a unique identifier to an address, the entrypoints of the manager can then look up the address with its assigned identifier. The assignment of identifiers to entrypoints is hard-wired during the compilation.

In the storage, the addresses could be stored in a mapping from a unique identifier

\begin{figure}[h]
\centering
  \includegraphics[width=0.9\textwidth]{figures/4-offline_tezos/interaction_modular.jpg}
	\caption{Interaction with a modular contract}
	\label{fig:interaction_modular}
\end{figure}

\subsubsection{Evaluation of the modular approach}
- fixes the problem of the monolithic approach, where calls to default cause problems -> mirrored interface can simply pass the parameter on as is to the parent and the extracted raw value to the assertion
- parent code doesn't have to be touched -> works for originated contracts
- flexibility -> case contracts independent of the rest; replace manager (with or without case contracts), parent with manager
- assertions can be bypassed in any case -> big security issue

\begin{itemize}
\item The address of the assertion contract needs to be provided in some way
	\begin{itemize}
	\item [a)] Parent storage contains the address of its assertion contract
		\begin{itemize}
		\item Parent contract needs to be modified (storage declaration, every storage access \& return value)
		\item Assertion contract must be originated first, so that address can be passed into initial storage of parent
		\item Baker needs to retrieve address from contract storage (no obvious standard way to do this - storages can look differently)\\
		 \verb|->| BigMap?
		\end{itemize}
	\item [b)] Address of the assertion contract is a parameter of the transaction
		\begin{itemize}
		\item Address must be known to the caller
		\item Decouples parent and assertion contract %\sout{(if calling assertion from parent is not necessary)}
		\item Safety issue: can be passed a contract with correct type that never returns a counterexample
		\item Parent contract doesn't need to be touched
		\end{itemize}
	\end{itemize}
\end{itemize}
